A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-16 documents/plm.tex
notes to self

@@

@@

Lots of quantitative and qualitative choices that ought to be explored.

>>>>

For each pixel, we choose the set of basis-vector pixels how?

For each time-step, we choose the set of training time steps how?

We specify what likelihood and what regularization?

We train the model how?

We choose the strength of the regularization how?

We do this for every pixel and every time step.
Implementation issues.

We construct the predicted images and the \name\ images how?

What does the interface look like?  What are the run times and so on?

@@

For each example, give the code and show the output and provide some discussion.

@@

Lots of quantitative and qualitative choices that ought to be explored.
These include what and what and what and what?
